---
title: "02_data_types"
author: "bjkim"
date: "2015년 10월 23일"
output: 
  html_document: 
    highlight: kate
    theme: cerulean
    toc: yes
---


# overview on Object and Attributes

## What's the Objects

 All the thing that you manipulate in R, all the things that we encounter in R are what might be called objects.

All the things are object.

## 5 atomic class of Object

R has 5 "atomic classes" of the objects. 

* character
* numeric
* integer
* complex
* logical

```{r, echo=FALSE,error=TRUE,prompt=TRUE}
  cTest <-"BJKIM"
  nTest <- 5
  iTest <- 3.3
  lTest <- FALSE
```

### Numeric
* decimal numbers such as 1,2,3,4,5,6.1,6.2

Special Numeric values

* **Inf** -  e.g) 1 / 0
  Inf can be used in ordinary calculation;

```{r, prompt=TRUE}
  1/Inf
```

* **NaN** - Undefined value. this value is also used for missing value 

```{r, prompt=TRUE}
  x<-0/0
  x
```

### integer

- natural numbers like 1,2,3 are called integer and also numeric.
- numbers can be integer when you specify "L"" suffix.


```{r,echo=TRUE,eval=TRUE,prompt=TRUE}
x<-1
is.integer(x)
is.numeric(x)

x<-1L
is.integer(x)
is.numeric(x)

```

### Character
- characters are just "texts"

```{r}
x<-"hi dude!"
is.character(x)
class(x)
```
### complex 

### logical

* True/False
* 0 is False. and any number greater than 0 is True.


## How to test what is the class of object

* `is.[\:class\:]\(\<object\>)` is the way of method to check the class.

```{r,echo=TRUE,eval=TRUE,prompt=TRUE}
    cTest <-"BJKIM"
    is.character(cTest)
    is.numeric(cTest)
    is.integer(cTest)
    is.complex(cTest)
    is.logical(cTest)
    class(cTest)
```


## Change the class of the objects

- `as.[:class:]\(\<object\>)` expression changes the class of specified object to [:class:]

```{r,echo=TRUE,eval=TRUE,prompt=TRUE}
x<-0:6
class(x)
as.numeric(x)
class(x)
as.logical(x)
class(x)
as.character(x)
class(x)

```

#### Nonsensical coercion result in NAs

```{r,echo=TRUE,eval=TRUE,prompt=TRUE}
x<-c("A","B","C")
y<-as.numeric(x)
y
y<-as.logical(x)
y
y<-as.complex(x)
y

```

## Attributes

each R objects can have attributes

* names, dimnames
* dimensions (e.g. matrices, arrays)
* class
* length
* other user-defined attributes/metadata

Attributes of an object can be accessed using the attributes() function.

### Names

* R object can have their own name.
* Name is very useful for writing readable code and self-describing objects
```{r,echo=TRUE,eval=TRUE,prompt=TRUE}
x<-1:3
names(x)
names(x)<-c("Milk","Coke","Water")
x
names(x)
```

* You can also give a name to list object
```{r,echo=TRUE,eval=TRUE,prompt=TRUE}
x<-list(a=1,b=2,c=3)
x
names(x)
```

* Matrice also can have names by using ```dimnames()```
```{r, echo=TRUE,eval=TRUE,prompt=TRUE}
m<-matrix(1:4,nrow=2,ncol=2)
dimnames(m) <-list(c("a","b"),c("c","d"))

```

## Objects

### Vector
  
* What's the Vector ?

    Vector is a container to contain data.
    vector can only store objects of same class
  
* How to create vector ?

    1. Vector is generated by `vector()` expression
  
        ```{r,echo=TRUE,eval=TRUE,prompt=TRUE}
        tVector<-vector(mode = "logical", length = 0)
        tVector
        ```

    2. c() function can also be used to create vectors of objects

        ```{r, echo=TRUE,eval=TRUE,prompt=TRUE}
        x<-c(0,1,2,0.5) ## numeric vector
        x<-c(TRUE,FALSE) ## logical vector
        x<-c(T,F) ## logical vector
        x<-c("a","b","c") ## characters
        x<-9:29 ## numeric, integer vector
        x<-c(1+0i,2+4i) ## complex vector
        ```
    3. you can create empty vector by
  
        ```{r,echo=TRUE,eval=TRUE,prompt=TRUE}
         vTest<- vector()
         is.vector(vTest)
        ```


### List ( Mixing different class of Objects)

* List is a Special case of vector which can cotain different objects of different classes.

* Lists are very important data type in R and you should get to know them well.

* Creating Lists

    * Creat List by ```list()```
    
    ```{r,echo=TRUE,eval=TRUE,prompt=TRUE}
    x<-list(1,"a",TRUE,1+4i)
    x
    ```
  
   * List is actually the group of different single vectors.
   
   * double bracket "[[" "]]" means that it is the nth element of the list
   * single bracket "[" "]" means the nth element of the vector.
   
### Matrix
   * matrices are vectors with a dimension attributes.
   * The dimension attribute is itself an integer vector of length 2 (nrow,ncol)

  * Creating Matrix by ```matrix()``` expression.
  
    ```{r,echo=TRUE,eval=TRUE,prompt=TRUE}
    x<-matrix(nrow=2,ncol=3)
    x
    dim(x)  # show the coluimns
    attributes(x) # show the attributes
    ```

  - Matrices are constructed **column-wise**.
  
    ```{r,echo=TRUE,eval=TRUE,prompt=TRUE}
    x<-matrix(1:6, nrow=2, ncol=3)
    x

    ```
  
  - You can also construct matrices **row-wise**  
    ```{r,echo=TRUE,eval=TRUE,prompt=TRUE}
    x<-matrix(1:6, byrow=TRUE,nrow=2, ncol=3)
    x

    ```   
    
    
  * Making Matrix by ```cbind()```, ```rbind()```
    ```{r,echo=TRUE,eval=TRUE,prompt=TRUE}
    x<-1:4
    y<-2:5
    z<-cbind(x,y)
    z
    z<-rbind(x,y)
    z
    ```
    

### factor

Factors are used to represent categorical data.
Factors can be unordered or ordered.

one can think of a factor as an integer vector where each integer has a label.

* Factors are treated specially by modelling function like ```lm()```,```glm()```
    those commands used for linear model.
    
    
* Using factors with labels is better than using inmtegers because factors are self-describing; having a variable that has values "Males" and "Females" is better than a variable that has values 1 and 2.

* Creating factor by `factor()`

```{r,echo=TRUE,eval=TRUE,prompt=TRUE}
  x<-factor(c("Male","Female","Unknown","Male")) 
  x
  table(x) # gave me frequency count of how many of each level there are
  unclass(x) # show the values defined for each class.
  attr(x,"levels")
```

  * What is level attribute ? n(categorical data)
  
  * ordering
  
    Order of the levels can be set using the levels argument to ```factor()```
  this can be important in linear modelling because the first level is used as the baseline level.
  
    the level value is setted by alphabetical order in default.
    
    however, you can customally set it by
    
    ```{r,echo=TRUE,eval=TRUE,prompt=TRUE}
    x<-factor(c("Male","Female","Unknown","Male"),levels=c("Unknown","Male","Female"))
    x
    unclass(x)
    ```

### Data Frames

Data frames are used to store tabular data

* They are represented as a special type of list where every element of the list has to have the same length.

* Each element of the list can be thought of as a column and the length of each element of the list is the number of rows

* Unlike matrices, data frames can store differen classes of objects in each column (just like lists); matrices must have every element be the same class.

* Data frames also have a special attribute called row.names

* Data frames are usually created by calling read.table() or read.csv()

* can be converted to a matrix by calling as.data.matrix()

```{r,echo=TRUE,eval=TRUE,prompt=TRUE} 
   x<-data.frame(foo=1:4, bar=c(T,T,F,F))
   x
   nrow(x)
   ncol(x)
     
```



## Missing Values

Missing values are denoted by NA or NAN for undefined mathmetical operations

* you can ask if the value is missing by

    ```{r,echo=TRUE,eval=TRUE,prompt=TRUE}
    x<-c("")
    is.na(x)
    ```
    
* NA value can also have class such as integer NA, character NA, etc.
    ```{r,echo=TRUE,eval=TRUE,prompt=TRUE}   
    class(x)
    ```
    
