---
title: "04_R_Basics"
author: "bjkim"
date: "2015년 10월 26일"
output: 
  html_document: 
    highlight: monochrome
    theme: flatly
    toc: yes
---

# Subsetting vector
  There are number of ways to extract subsets of R objects
  
* "**[**", always returns an object of the same class as the original; can be used to select more than one elements(there is one exceptions)

* **[[**, is used to extract elements of a list or a data frame :
    it can only be used to extract a single element and the class of the returned object will not necessarily be a list or data frame.

* **$**, is used to extract elements of a list or data frame by name :
    semantics are simillar to hat of "[["

```{r,echo=TRUE,eval=TRUE,prompt=TRUE}
  x<-c("a","b","c")
  x
  x[1]  ## numerical index
  x[1:2]
  x[x > "a"] # only select elements larger than a
  u <-x > "a"
  u ## logical index
  
  x[u]
  

```

# subsetting Lists

```{r,echo=TRUE,eval=TRUE,prompt=TRUE}
  x<-list(foo=1:4, bar=0.6)
  x
  x[[1]]
  x$bar
  x["bar"]
  x[["bar"]]
  

```

# subsetting nested elements of a list

```{r,echo=TRUE,eval=TRUE,prompt=TRUE}
  x<-list(a=list(10,12,14),b=c(3,14,8))
  x[[c(1,3)]]
  x[[1]][[3]]
```

# subsetting matrix

* Matrices can be subsetted in the usual way with (i,j) type of index
  where i=first index and j is the second index.
```{r,echo=TRUE,eval=TRUE,prompt=TRUE}
  x<-matrix(1:6,2:3)
  x[1,2]
  x[2,1]
  
```

* indices can also be missing. if the index is missing, the expression prints all the elements of missing index ( think that shows all the values of the column / rows )

```{r,echo=TRUE,eval=TRUE,prompt=TRUE}
    x[1,]
    x[,2]
```

*  by default, subsetting matrixs prints vector with length n. it was turned off by setting drop=FALSE 
```{r,echo=TRUE,eval=TRUE,prompt=TRUE}
    x[1,]
    is.vector(x[1,])
    x[1,,drop=FALSE]
    is.vector(x[1,,drop=FALSE])
    is.matrix(x[1,,drop=FALSE])

```

# subsetting -Partial matching

* IF you do not rememebr the entire name of column or row, You can use partial matching with **[[** and **$**

```{r,echo=TRUE,eval=TRUE,prompt=TRUE}
    x<-list(merong=1:5)
    x$m
    x[["m"]]
    x[["m",exact=FALSE]]
```

# subsetting - Removing missing values

* a common tak is to remove missing values (NAs)

```{r,echo=TRUE,eval=TRUE,prompt=TRUE}

    x<-c(1,2,NA,4,NA,5,NA)
    bad<-is.na(x)
    bad # which element is NA (T/F)
    x[bad] # print only True
    x[!bad] # print only false
```


* ```complete.case() function ```
    ```the complete.case()``` function return a logical vector indicating which cases are complete, i.e., have no missing values
  
    ``` {r,echo=TRUE,eval=TRUE,prompt=TRUE}
    x<-c(1,2,NA,4,5,NA)
    y<-c("a","b",NA,"d",NA,"f")
    good<- complete.cases(x,y)
    good
    x[good]
    y[good]
    
    ```

* you can also omit missing values from data.frame using ```complete.case``` 

    ``` {r,echo=TRUE,eval=TRUE,prompt=TRUE}
    airquality[1:6,]
    good<-complete.cases(airquality)
    airquality[good,][1:6,]
    ```
    
# vectorized Operation

* Many operations in R are vectorized making code more efficient, concise, and eaiser to read.

    e.g) arismetic operation such as add(**+**), substraction(**-**), multipllication(**\***) and  divide(**/**)

```{r,echo=TRUE,eval=TRUE,prompt=TRUE}
  x<-1:4;
  y<-6:9;
  x+y # 1+6, 2+7, 3+8, 4+9
    
  x > 2
  y==8
  x*y
  x/y

```

# vectirized matrix operation
```{r,echo=TRUE,eval=TRUE,prompt=TRUE}
  x<-matrix(1:4,2,2);
  y<-matrix(rep(10,4),2,2)
  x*y ## element-wise multiplication. this is not matrix multiplication
  
  x/y
  
  x %*% y ## true matrix multiplication
```
# SWIRL
-
-
-
-