---
title: "Statistical_Backgrounds_for_regression"
author: "Byungju Kim"
date: "2018년 11월 15일"
output:
  bookdown::html_document2: 
    theme: united
    toc: yes
    toc_depth: 4
    toc_float: yes
    code_folding: hide
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Data Distribution

* Probability Distribution

```{r distribution,meassage=F}
 require(HistData,quietly=T)
 set.seed(7777)
 df<-data.frame(id=1:2000,height=rnorm(2000,mean=65,sd=2))
 df$class<-"normal distribution"
 df2<-data.frame(id=1:2000,height=c(rnorm(1200,mean=70,sd=1),rnorm(600,mean=67,sd=3),rnorm(200,mean=68.5,sd=1)))
 df2$class<-"not a normal distribution"

 DST<-rbind.data.frame(df,df2)
 rm(df,df2)
 p<-ggplot(DST,aes(height,fill=class,color=class))+geom_histogram(position="identity",alpha=0.7,bins=40) + scale_fill_manual(values=c("#722F37","#008080")) + scale_color_manual(values=c("#722F37","#008080")) + theme_bw() + theme(legend.position=c(0,1),legend.justification=c(0,1),legend.background=element_blank(),legend.title=element_blank())

p
```


## Discrete Distribution

### Benford distribution

The [Benford Distribution](http://en.wikipedia.org/wiki/Benford_distribution) is the distribution of the first digit of a number. It is due to Benford 1938[1] and Newcomb 1881

```{r New-come_Benford}
 library(VGAM)
 benfold<-data.frame(number=1:9,prob=dbenf(c(1:9)))
 bf_dist<-ggplot(benfold,aes(number,prob)) + geom_bar(stat="identity") + theme_bw() + ggtitle("benford-newcome distribution")
 
 bf_dist
```

the probability of first digit from random selection of a number from a table of physical constants or statistical data.

$$
\begin{equation}
P{d} = \frac{1 +\frac{1}{d}}{ln(10)}
(\#eq:benfold)
\end{equation}
$$

## Continuous distribution


**Normal distribution** means and variance

* Non-normal distribution

1. beta distribution

```{r beta distribution}
        

```
2. Exponential Distribution
3. gamma distribution
4. inverse gamma distribution
5. Log Normal distribution
6. Logistic distribution
7. Maxwell-Boltzmann distribution
8. Poisson distribution
9. Skewed Distribution
10. Symmetric distribution
11. Uniform distribution
12. Unimodel distribution
13. Weibull-Distribution

**Linear transformation** 

**Lognormal distribution**


## Reference

1. Benford, F. (1938) The Law of Anomalous Numbers. Proceedings of the American Philosophical Society, 78, 551–572.
2. Newcomb, S. (1881) Note on the Frequency of Use of the Different Digits in Natural Numbers. American Journal of Mathematics, 4, 39–40.