---
ptitle: "01_R_Input_and_Evaluation"
author: "bjkim"
date: "2015년 10월 23일"
output: 
  html_document: 
    highlight: pygments
    theme: readable
    toc: yes
---
# R Basics

## Input and Output

### Input

* prompt

    ```
    >
    ```

    prompt is the sign to show R is ready to receive the input.
    you can put the expression(commands) here.

* expression

    the things we type into the R prompt are called *expression*
    For easy uderstanding, think expression as a command.

    anything you entered in the prompt is "expression"

    ```{r expression, echo=TRUE,eval=TRUE, error=TRUE,prompt=TRUE}
    hello

    ```
  
    but R can't understand real "human words". 
  
* assignment (<-)
    
    arrow, assignment symbol assigned a value to specific variable.

    ```{r, echo=TRUE,eval=TRUE, prompt=TRUE}
    x<-5  # assign 1 to x
    x     # check the value of "x""
    ```

* comment (\#)

    the number symbol, hash symbol ,\# character indicates a coment
    Anything to the right of \# (including the \# itself) is ignored 
    
    in above expression, \# sentences explains the code.
    
### Output
  If a complete expression is entered at the prompt, the output shows the result of your expression.
  
````{r, echo=TRUE,eval=TRUE,prompt=TRUE}
    x  # print x
    print(x) ## explicit priinting
````

* the output, [1] 5, means that x is a vector and 5 is the first element.
  sometimes, the output does not print anything.

    ````{r, echo=TRUE,eval=TRUE,prompt=TRUE}
    x <- 1:20 # assign 1 
    print(x) ## explicit priinting
    ````

    colon operator is used to generate sequence of numbers.
    
## Arithmetics with R

- Addition `+`
```{r addition}
 1+1
```

- Substraction `-`

```{r substraction}
 2-1

```

- Multiplication `*`

```{r Multiplication}
 3 * 3
```

- Division `/` and remainders(Modulo) `%%`

```{r division}
  ## division
  10/3 

  ## Modulo
  10%%3
```

- Exponential `^`

```{r}
  ## Exponential
  2^4

```
