---
title: "03_Read/Write_data"
author: "bjkim"
date: "2015년 10월 26일"
output: 
  html_document: 
    highlight: tango
    theme: united
    toc: yes
---

# Reading data

## read.table and read.csv, for reading tabular data.

### read.table
* most commonly used function for reading files.
* important Arguments
    + **file**, the name of a file, or a connection. indicating the data to be read.
    + **header**, logical indicating if the file has a header line.
    + **sep**, a string indicating how the columns are separated.
    + **colClasses**, a character vector indicating the class of each column in the dataset
    + **nrows**, the number of rows in the dataset
    + **comment.char**, a character string indicating the commenting character
    + **skip**, the number of lines to skip from the beginning
    + **stringsAsFactors**, should character variables to be coded as factor?

```{r, echo=TRUE,error=TRUE,prompt=TRUE,eval=FALSE}
  data<-read.table("foo.txt")
```

R will automatically 

* skip lines that begin with a #
* figure out how many rows there are (and how much memory needs to be allocated)
* figure what type of variable is in each column of the table telling R all these things directly makes R run faster and more efficiently


### read.csv

* Initially, this function is same with ```read.table()``` 
* but the default separator is ```,```

### Reading Large dataset using read.table

* read the help page by ```?help(read.table)``` which gave you numerous hints.
* make a rough calculation of memory required to store your data.
    if the dataset is larger than the amount of the RAM on your computer, you can probably stop right here.
* Set ```comment.char=""``` if there are no commented lines in your file.

* **colClasses** are very important if you want read file more faster than default read.table.  

* **Set nrows**. argument set nrows helps to reduce the memory usage.
* knowing the system you used is useful way to handle large dataset
    + How much memory is available?
    + what other applications are in use?
    + are there other users logged into the same system?
    + what operating system?
    + is the computer 32bit or 64bit ?
    
## Calculating Memory Requirements

* if you have 1,500,000 x 120 numeric data, 1,5000,000x120x8bytes/numeric memory is required.
* 2^20^ byte = 1MB
    
## ```readLines()```, for reading lines of a text file

```{r, echo=TRUE,error=TRUE,prompt=TRUE,eval=TRUE}
con<-file("./data/Real.first.6game")
x<-readLines(con,10)
x
```
## ```source()```, for reading in R code files (inverse of dump)

## ```dget```, for reading in R code files (inverse of dput)

## ```load```, for reading in saved workspaces.

## ```unserialize```, for reading single R objects in binary form


# Writing data

## ```dumping``` and ```dputing```, for textual format.

* unliking writing out a table or csv file, ```dump``` and ```dputing``` preserve the *metadata* (sacrificing some readability), so that another user doesn;t have to specify it all over again 

* easy to check the corruption and fix the problem.

* Downside - the format is not very space-efficient.

### dput-ting R objects

```{r, echo=TRUE,error=TRUE,prompt=TRUE,eval=TRUE}
  y<-data.frame(a=1,b="a")
  dput(y)
  dput(y,file="y.md")
  new.y<-dget("y.md")
  new.y
```

### dumping R Objects

* multiple objects can be deparsed using the dump function and read back in using ```source()```.

```{r, echo=TRUE,error=TRUE,prompt=TRUE,eval=TRUE}
x<-"foo"
y<-data.frame(a=1,b="a")
dump(c("x","y"),file="y.md")
rm(x,y)
source("y.md")
y
 x 
```


# Interfaces to the outside world
Data are read in using connection interfaces.
connections can be made to files (most common) or to other more exotic things

* file
* gzfile
* bzfile
* url

## File connections

```{r, echo=TRUE,error=TRUE,prompt=TRUE,eval=TRUE}
str(file)
```
* description is the name of file
* open is a code indicating
  * "r", for read only
  * "w", for writing
  * "a", apending
  * "rb","wb","ab" - reading, writing, apending in binary mode (windows)
  
### open connection
```{r, echo=TRUE,error=TRUE,prompt=TRUE,eval=TRUE}
  con<-file("./y.md","r")
  data<-read.csv(con)
  close(con)
```


```{r, echo=TRUE,error=TRUE,prompt=TRUE,eval=TRUE}
 
  data<-read.csv("./y.md","r") # same with above chunks

```

### close connection

### Reading from web
```{r, echo=TRUE,error=TRUE,prompt=TRUE,eval=TRUE}
con<-url("http://sports.media.daum.net/sports/worldsoccer/netizen/talk/")
x<-readLines(con)
```

### Subsetting R Objects

