---
title: "Linear Algebra : Vector and its space"
author: "bjkim"
date: '2016 12 19 '
output: html_document
---

# Objects
- Knows the vector
- understand how to calculate vectors
- 
# Introduction about Vectors

## Definition of Vectors 

**Vector** is a quantity having direction as well as **magnitude**, especially as determining the position of one point in space relative to another. e.g) velocity of 5 athletes. magitude ( 5 mph ) + direction ( west and or right. )

```{r, echo=FALSE}
set.seed(1234)
  data<-data.frame(xBegin=sample(10,5),xEnd=sample(10,5), yBegin=1:5, yEnd=1:5)

```

## Visualizing Vector

- vectors are represented as arrows, length for magnitude and direction for head.

```{r, echo=FALSE, message=FALSE}

  require(ggplot2)
  p<-ggplot(data,aes(xBegin,yBegin)) + geom_point()
  p<-p+ geom_segment(aes(x=xBegin,xend=xEnd,y=yBegin,yend=yEnd),size=2,arrow=arrow(length=unit(0.5,"cm")))
  p<-p+theme_bw() + xlab("Velocity") + ylab("Sample No.")
  p
  
```

in typical mathmatical equation, vector is denoted as $$\vec{x} = (5,0) = \left( \begin{array}{c} 5 \\ 0 \end{array}\right)$$.

# Vector Space

$\begin{array}{c} R^n \\ \mathbb{R}^n \end{array} \Big\}$ n-Dimensional Real coordinate space.

$$\begin{equation}
  \left( \begin{array}{c}
  x_{1} \\  
  x_{2} \\  
  \vdots \\
  x_{n}
  \end{array} \right)
  \end{equation}$$
 
# Vector Arithmetic

$$\vec{a} = \left( \begin{array}{c} 6 \\-2 \end{array} \right), \vec{b} = \left( \begin{array}{c} -4 \\4 \end{array} \right)$$

### Adding vectors,

$$\vec{a} + \vec{b} =  \left( \begin{array}{c} 6 + -4 \\ -2 + 4 \end{array} \right)$$

### Substrating vectors,

### Multipying vectors by scalars

$$3 \times \vec{a} = 3 \times \left( \begin{array}{c} 6 \\-2 \end{array} \right) = \left( \begin{array}{c} 3 \times 6 \\ 3 \times -2 \end{array} \right)$$

- 3 is scalar, which denotes the orientation and magnitude of the small vector space.

## Unit vector notation.

- vector of length 1.
- normally, denoted by a lowercase letter with a "hat"

$$\hat{i}=\left( \begin{array}{c} 1 \\ 0 \end{array} \right)$$

$$\hat{j}=\left( \begin{array}{c} 0 \\ 1 \end{array} \right)$$

Any two dimensional vectors are calculated by 2 unit vector, i and j.